\textbf{Discovery of a disrupting open cluster in the Milky Way halo:\\ a recent star formation event in the leading arm of the Magellanic stream?}

### 2018-11-06 ms.tex
oops conclusions

Given its extragalactic origin, its proximity to the Magellanic stream suggests that \clustername\ could have formed from this gas.

Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys provides a wealth of information about our Galaxy and stellar halo.

>>>>

We have identified a young, metal-poor stellar association in the Galactic halo --- named \clustername\ --- with an age $\tau \approx \clage$, heliocentric distance $D \approx \cldist$, and metallicity $\feh \approx \clfeh$.
At its present day sky position, and at large distances, all significant quantities of \hi are associated with the leading arm of the Magellanic gas stream and thus it plausibly formed from Magellanic stream gas.
The age of the cluster is broadly consistent with the time it would have most recently crossed the Galactic midplane, suggesting the possibility that interaction with the Milky Way disk or tidal compression could have triggered this star formation event.
Previously studies have detected young stars in the Leading Arm and gas in the periphery of the Magellanic Clouds \citep{Casetti-Dinescu:2014, Moni-Bidin:2017}, however, this is the first time that an entire star cluster has been detected so far from the Clouds.

The discovery of \clustername\ provides a critical distance constraint to the Magellanic stream and will aid future Magellanic system and Milky Way modeling efforts.
It also provides an opportunity to study star formation in a unique environment, unlike that of the Milky Way disk or any other cluster-forming region.
The serendipitous discovery of this cluster is a reminder that the combined value of the \gaia\ data with deep, large-area imaging surveys provides a wealth of information about our Galaxy and stellar halo.
